---
title: 'DS 3606 :: Case Study 1'
author: "Brandon Sucrese"
date: "6/25/2021"
---

Introduction: Welcome to the brewery and beer analysis. The following code will walk through important discovers about beer. We will be looking at quantity of breweries and the distribution of beers' alcohol content. We will also explore the relationship between alcohol content and bitterness as well as how the style of beer effects these variables. Lastly we will look into which states have the highest different in alcohol among their beers. Understanding how beer works and it's finer details, always us to better understand beers in the future.

Code Summary: Reads in necessary libraries.
```{r}
library(naniar)
library(tidyverse)
library(mice)
library(ggplot2)
library(htmlwidgets)
library(caTools)
library(class)
library(caret)
library(stats)
library(dplyr)
library(agricolae)
```

Code Summary: Reads in the beer and breweries data sets. Sets the variables to the correct type and summaries the two data sets.
```{r}
beer = read_csv("https://raw.githubusercontent.com/BivinSadler/MSDS_6306_Doing-Data-Science/Master/Unit%208%20and%209%20Case%20Study%201/Beers.csv") 
breweries = read.csv("https://raw.githubusercontent.com/BivinSadler/MSDS_6306_Doing-Data-Science/Master/Unit%208%20and%209%20Case%20Study%201/Breweries.csv")
breweries$State = as.factor(breweries$State)  ## Sets the state variable to a factor
summary(beer) ## Summarizes the beer data set
summary(breweries) ## Summarizes the breweries data set
```

Code Summary: Plots the amount of breweries in each State.
```{r}
breweries %>% ggplot(aes(x=reorder(State, State, function(x) -length(x)))) + geom_bar() + ggtitle("Breweries by State") + xlab("States")
```

Code Summary: Merges the beer and breweries data set together and relabels the data set.
```{r}
beer_comp = merge(beer, breweries, by.x = "Brewery_id", by.y = "Brew_ID")  ## Merges the beer and breweries data sets
colnames(beer_comp)[which(names(beer_comp) == "Name.x")] <- "Beer_Name"  ## Renames column to Beer_Name
colnames(beer_comp)[which(names(beer_comp) == "Name.y")] <- "Brewery_Name"  ## Renames column to Brewery_Name
colnames(beer_comp)[which(names(beer_comp) == "Brewery_id")] <- "Brewery_ID"  ## Renames column to Brewery_ID
```

Code Summary: Graphs missing data and shows first and last observations in the full beer data set.
```{r}
imp_beer_comp = beer_comp  ## Changes beer_comp to imp_beer_comp
gg_miss_var(imp_beer_comp)  ## Graphs missing values by variable
head(imp_beer_comp, n=10)  ## Displays first 10 observations
tail(imp_beer_comp, n=10)  ## Displays last 10 observations
```

Code Summary: Creates a new data set of Median ABV by state. Graphs and summarize this data set.
```{r}
State_ABV = imp_beer_comp %>% filter(!is.na(imp_beer_comp$ABV))  ## Filters out any rows with missing values for ABV

State_ABV = aggregate(x = State_ABV$ABV,  ## Creates data set of all the states and their corresponding median ABV values
          by = list(State_ABV$State),
          FUN = median)

colnames(State_ABV)[which(names(State_ABV) == "x")] <- "Median_ABV"  ## Renames column to Median_ABV
colnames(State_ABV)[which(names(State_ABV) == "Group.1")] <- "State"  ## Renames column to State

State_ABV %>% ggplot(aes(x=reorder(State, -Median_ABV), y=Median_ABV, color=State)) +  ## Graphs Median ABV by State in order
  geom_col() + ggtitle("Median ABV by State") + xlab("State") + ylab("Median ABV")  

a = which.max(State_ABV$Median_ABV)  ## Finds and displays the state with the greatest median ABV
State_ABV[a,]
b = which.min(State_ABV$Median_ABV)  ## Finds and displays the state with the lowest median ABV
State_ABV[b,]
```

Code Summary: Finds and displays the beer with highest ABV and IBU values. Also finds and displays the beer with the lowest ABV and IBU values.
```{r}
c = which.max(imp_beer_comp$ABV)  ## Finds and displays beer with the highest ABV value
imp_beer_comp[c,]
d = which.max(imp_beer_comp$IBU)  ## Finds and displays beer with the highest IBU value
imp_beer_comp[d,]

e = which.min(imp_beer_comp$ABV)  ## Finds and displays beer with the lowest ABV value
imp_beer_comp[c,]
f = which.min(imp_beer_comp$IBU)  ## Finds and displays beer with the lowest IBU value
imp_beer_comp[d,]
```

Code Summary: Summarizes the ABV value and plots ABV distribution by state.
```{r}
summary(imp_beer_comp$ABV)  ## Summarizes ABV data
imp_beer_comp %>% ggplot(aes(x=ABV, color=State)) + geom_histogram() + ggtitle("ABV Distribution") ## Histogram plot of ABV distribution
imp_beer_comp %>% ggplot(aes(x=ABV, color=State)) + geom_histogram() +  ## Histogram plot of ABV distribution by state histogram
  facet_wrap(~State) + ggtitle("ABV Distribution by State")
imp_beer_comp %>% ggplot(aes(x=State, y=ABV, color=State)) + geom_boxplot() + ggtitle("ABV Distribution by State")  ## Boxplot of ABV distribution by state
```

Code Summary: Plots the relationship between ABV and IBU
```{r}
imp_beer_comp %>% ggplot(aes(x=ABV, y=IBU, color=State)) + geom_point() + ggtitle("ABV vs IBU")  ## Scatter plot comparing ABV and IBU (Points colored by state)
imp_beer_comp %>% ggplot(aes(x=ABV, y=IBU)) + geom_point() + ggtitle("ABV vs IBU") + geom_smooth(method = "lm") ## Scatter plot comparing ABV and IBU with a linear regression line
```

Code Summary: Creates a data set of just IPA and Ale style of beers and plots this new data.
```{r}
IPA_Beer = imp_beer_comp %>% filter(str_detect(imp_beer_comp$Style, "IPA"))  ## Creates data set of just IPA beers
IPA_Beer$Style = "IPA"
Ale_Beer = imp_beer_comp %>% filter(str_detect(imp_beer_comp$Style, "Ale"))  ## Creates data set of just Ale beers
Ale_Beer$Style = "Ale"
IPA_Ale_Beer = rbind(IPA_Beer, Ale_Beer)  ## Combines the IPA and Ale beer data sets together
IPA_Ale_Beer = na.omit(IPA_Ale_Beer) ## Removes any missing values from the data set

IPA_Ale_Beer %>% ggplot(aes(x=ABV, y=IBU, color=Style)) + geom_point() + ggtitle("ABV vs IBU") ## Scatter plot of IBU and ABV, style of Beers are colored
```

Code Summary: Splits the data into a training and test set. Runs a KNN classification model on the IPA and Ale beer data set.
```{r}
set.seed(1)  ## Sets the seed
sample = sample.split(IPA_Ale_Beer[,1], SplitRatio = .70)  ## Splits the data using 30/70 ratio
beer_train = subset(IPA_Ale_Beer, sample == TRUE)  ## Creates training set
beer_test  = subset(IPA_Ale_Beer, sample == FALSE)  ## Creates test set

v1 = beer_train[,6]  ## Creates classifiers references of IBA and IBU
pred = knn(beer_train[,c('ABV', 'IBU')], beer_test[,c('ABV', 'IBU')], v1, k=2, prob = TRUE)  ## Creates data set of predictions using the KNN model for the style of beers (IPA vs Ale)
actual = beer_test$Style  ## Creates data set of the actual style of the beers
confusionMatrix(pred,as.factor(actual))  ## Creates a confusion matrix of the predicted and actual style of the beers
```

Code Summary: Runs an ANOVA and Tukey test to determine which States have significant difference in ABV.
```{r}
anova_beer = imp_beer_comp %>% filter(!is.na(imp_beer_comp$ABV))  ## Filters out all NA values in ABV
anova_results = aov(ABV ~ State, data = anova_beer)  ## ANOVA test for ABV between all States
summary(anova_results)  ## Summarizes the ANOVA results (results are significant)

HSD_results<-HSD.test(anova_results,"State", group=FALSE)  ## Runs Tukey pairwise comparison test
state_comparison = HSD_results$comparison  ## Makes data set related to comparisons including pvalues
sign_comp = filter(state_comparison, pvalue <= .05)  ## Makes data set of only comparison at are significant (pvalues <= 0.5)
print(sign_comp)  ## Prints all significant comparisons
```
